Title of submission to PLOS journal

### 2019-08-23 docs/manuscript_draft.Rmd
real citations

Understanding the mechanisms underlying parental care are critical to circumventing issues with parent-newborn bonding as well, where ultimate explanations are obvious, but specific mechanisms remain elusive.

The rock dove (_Columba livia_) is an ideal system to characterize changes in genetic expression during parental care transitions because: 1) ample genomic resources are available, including a complete annotated genome assembly (Gillespie et al. 2013; Shapiro et al. 2013) and methodology concerning reproductive physiology and behavior (Dong et al. 2012); and 2) rock doves are prolific, year-round breeders that thrive in captivity, making observation, manipulation, and sampling highly feasible year-round.

@@

Rock doves are socially monogamous and offer bi-parental care, making inter- and intra-sexual comparisons possible. Birds offer two important behavioral transition points into parental care: the incubation of eggs and the caring for chicks. This produces two unique opportunities to study how the brain transitions into two different suites of parental care behaviors. Additionally, rock doves exhibit a parental care strategy analogous to mammals in that they, too, ‘lactate’ to feed their young (Gillespie et al. 2011, 2012). This lactation, unlike simple regurgitation of food, consists of the production and sloughing off of skin cells inside the crop sac of females and males, creating a protein-rich milk-like substance on which they rear their chicks. Many functional similarities between rock dove and mammalian lactation exist concerning the mediation of this event by the hormone prolactin (Dumont 1965). Additionally, like mammalian milk, rock dove milk delivers essential immunoglobulins and nutritional benefits to young, aiding in their immune function and development of microbiota (Gillespie et al. 2012). Thus, because rock doves incubate eggs and exhibit mammalian-like mediation and function of lactation for young, they have the potential to serve as a powerful theoretical bridge to understand the neurobiology of both avian and mammalian transitions into parental care.

@@

Here are two sample references: @Feynman1963118 [@Dirac1953888].

@@

# Metadata and extras

## Funding Statment

@@

>>>>

Understanding the mechanisms underlying parental care are critical to circumventing issues with parent-newborn bonding as well, where ultimate explanations are obvious, but specific mechanisms remain elusive. The rock dove (_Columba livia_) is an ideal system to characterize changes in genetic expression during parental care transitions because: 1) ample genomic resources are available (Gillespie et al. 2013), including a complete annotated genome assembly @Shapiro1063 and methodology concerning reproductive physiology and behavior (Dong et al. 2012); and 2) rock doves are prolific, year-round breeders that thrive in captivity, making observation, manipulation, and sampling highly feasible year-round.

@@

Rock doves are socially monogamous and offer bi-parental care, making inter- and intra-sexual comparisons possible. Birds offer two important behavioral transition points into parental care: the incubation of eggs and the caring for chicks. This produces two unique opportunities to study how the brain transitions into two different suites of parental care behaviors. Additionally, rock doves exhibit a parental care strategy analogous to mammals in that they, too, ‘lactate’ to feed their young (Gillespie et al. 2011, 2012). This lactation, unlike simple regurgitation of food, consists of the production and sloughing off of skin cells inside the crop sac of females and males, creating a protein-rich milk-like substance on which they rear their chicks. Many functional similarities between rock dove and mammalian lactation exist concerning the mediation of this event by the hormone prolactin (Dumont 1965). Additionally, like mammalian milk, rock dove milk delivers essential immunoglobulins and nutritional benefits to young, aiding in their immune function and development of microbiota @Gillespie2012. Thus, because rock doves incubate eggs and exhibit mammalian-like mediation and function of lactation for young, they have the potential to serve as a powerful theoretical bridge to understand the neurobiology of both avian and mammalian transitions into parental care.

@@

@@

<!--

# Funding Statment

@@

-->

### 2019-08-23 docs/manuscript_draft.tex
real citations

Understanding the mechanisms underlying parental care are critical to
circumventing issues with parent-newborn bonding as well, where ultimate
explanations are obvious, but specific mechanisms remain elusive.

The rock dove (\emph{Columba livia}) is an ideal system to characterize
changes in genetic expression during parental care transitions because:
1) ample genomic resources are available, including a complete annotated
genome assembly (Gillespie et al.~2013; Shapiro et al.~2013) and
methodology concerning reproductive physiology and behavior (Dong et
al.~2012); and 2) rock doves are prolific, year-round breeders that
thrive in captivity, making observation, manipulation, and sampling
highly feasible year-round.

@@

Rock doves are socially monogamous and offer bi-parental care, making
inter- and intra-sexual comparisons possible. Birds offer two important
behavioral transition points into parental care: the incubation of eggs
and the caring for chicks. This produces two unique opportunities to
study how the brain transitions into two different suites of parental
care behaviors. Additionally, rock doves exhibit a parental care
strategy analogous to mammals in that they, too, `lactate' to feed their
young (Gillespie et al.~2011, 2012). This lactation, unlike simple
regurgitation of food, consists of the production and sloughing off of
skin cells inside the crop sac of females and males, creating a
protein-rich milk-like substance on which they rear their chicks. Many
functional similarities between rock dove and mammalian lactation exist
concerning the mediation of this event by the hormone prolactin (Dumont
1965). Additionally, like mammalian milk, rock dove milk delivers
essential immunoglobulins and nutritional benefits to young, aiding in
their immune function and development of microbiota (Gillespie et
al.~2012). Thus, because rock doves incubate eggs and exhibit
mammalian-like mediation and function of lactation for young, they have
the potential to serve as a powerful theoretical bridge to understand
the neurobiology of both avian and mammalian transitions into parental
care.

@@

Here are two sample references: {[}1,2{]}.

@@

\hypertarget{metadata-and-extras}{%
\section{Metadata and extras}\label{metadata-and-extras}}

\hypertarget{funding-statment}{%
\subsection{Funding Statment}\label{funding-statment}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Collaborative Research: RUI: The Neural Basis of Becoming a Parent:
  From Genotype to Phenotype. NSF-IOS:1455957.
\end{enumerate}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Feynman1963118}{}%
1. Feynman R, Vernon Jr. F. The theory of a general quantum system
interacting with a linear dissipative system. Annals of Physics.
1963;24: 118--173.
doi:\href{https://doi.org/10.1016/0003-4916(63)90068-X}{10.1016/0003-4916(63)90068-X}

\leavevmode\hypertarget{ref-Dirac1953888}{}%
2. Dirac P. The lorentz transformation and absolute time. Physica.
1953;19: 888--896.
doi:\href{https://doi.org/10.1016/S0031-8914(53)80099-6}{10.1016/S0031-8914(53)80099-6}

>>>>

Understanding the mechanisms underlying parental care are critical to
circumventing issues with parent-newborn bonding as well, where ultimate
explanations are obvious, but specific mechanisms remain elusive. The
rock dove (\emph{Columba livia}) is an ideal system to characterize
changes in genetic expression during parental care transitions because:
1) ample genomic resources are available (Gillespie et al.~2013),
including a complete annotated genome assembly {[}1{]} and methodology
concerning reproductive physiology and behavior (Dong et al.~2012); and
2) rock doves are prolific, year-round breeders that thrive in
captivity, making observation, manipulation, and sampling highly
feasible year-round.

@@

Rock doves are socially monogamous and offer bi-parental care, making
inter- and intra-sexual comparisons possible. Birds offer two important
behavioral transition points into parental care: the incubation of eggs
and the caring for chicks. This produces two unique opportunities to
study how the brain transitions into two different suites of parental
care behaviors. Additionally, rock doves exhibit a parental care
strategy analogous to mammals in that they, too, `lactate' to feed their
young (Gillespie et al.~2011, 2012). This lactation, unlike simple
regurgitation of food, consists of the production and sloughing off of
skin cells inside the crop sac of females and males, creating a
protein-rich milk-like substance on which they rear their chicks. Many
functional similarities between rock dove and mammalian lactation exist
concerning the mediation of this event by the hormone prolactin (Dumont
1965). Additionally, like mammalian milk, rock dove milk delivers
essential immunoglobulins and nutritional benefits to young, aiding in
their immune function and development of microbiota {[}2{]}. Thus,
because rock doves incubate eggs and exhibit mammalian-like mediation
and function of lactation for young, they have the potential to serve as
a powerful theoretical bridge to understand the neurobiology of both
avian and mammalian transitions into parental care.

@@

@@

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Shapiro1063}{}%
1. Shapiro MD, Kronenberg Z, Li C, Domyan ET, Pan H, Campbell M, et al.
Genomic diversity and evolution of the head crest in the rock pigeon.
Science. American Association for the Advancement of Science; 2013;339:
1063--1067.
doi:\href{https://doi.org/10.1126/science.1230422}{10.1126/science.1230422}

\leavevmode\hypertarget{ref-Gillespie2012}{}%
2. Gillespie MJ, Stanley D, Chen H, Donald JA, Nicholas KR, Moore RJ, et
al. Functional Similarities between Pigeon `Milk' and Mammalian Milk:
Induction of Immune Gene Expression and Modification of the Microbiota.
Salmon H, editor. PLoS ONE. Public Library of Science; 2012;7: e48363.
doi:\href{https://doi.org/10.1371/journal.pone.0048363}{10.1371/journal.pone.0048363}
